Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-04-27 chi/piecework/presentation/presentation.tex
gave up and went with keynote
notes and rough roadmapping is in the document
latex chi presentation draft (in progress)

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor}
\usepackage[citestyle=author,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

@@

\begin{frame}
\titlepage
\end{frame}

% PAPER ROADMAP
% Open problems in crowdsourcing: complexity, decomposition, relationships
% Piecework!
% Wait what's piecework again
% Some cool case studies: 
%     airy's computers
%     domestic/farmhand labor
%     matchstick girls
%     industrial workers
% Okay let's get into this
% Complexity limits
%     what did crowdsourcing say?
%     what did piecework say?
%     comparisons?
%     implications?
% Decomposition limits
%     what did crowdsourcing say?
%     what did piecework say?
%     comparisons?
%     implications?
% Worker relationships
%     what did crowdsourcing say?
%     what did piecework say?
%     comparisons?
%     implications?
% Discussion
%     this is a very tricky thing to do, predicting the future
%     anyway let's predict the future: utopian/dystopian visions
%     Research agendas! go go gadget contextual analysis

\section{Introduction}

\begin{frame}{Open problems in crowdsourcing}
\begin{itemize}[<+- | alert@+>]
  \item Complexity~\cite{suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}
  \item Decomposition
  \item Relationships
\end{itemize}
\end{frame}

\begin{frame}{Emerging field of on--demand work}
\begin{itemize}[<+- | alert@+>]
  \item what's that about??
\end{itemize}
\end{frame}

>>>>

\usepackage{tikz,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,enumitem}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\renewcommand\textbullet{\ensuremath{\bullet}}
\definecolor{stanfordRed}{HTML}{8C1515}
% \mode<presentation>{
  % \usetheme{metropolis}
  \usecolortheme{seagull}

@@

\hypersetup{
  colorlinks = true,
  % linkcolor = blue,
  citecolor = blue
}

\def\labelitemi{--}

% \let\oldcite=\textcite
% \renewcommand{\textcite}[1]{\textcolor[rgb]{.2,.2,.9}{[\oldcite{#1}]}}

@@

\begin{frame}
\titlepage
\end{frame}
% \renewcommand\multicitedelim{\addsemicolon\space}

% \setbeamercovered{transparent}

\section*{Introduction}

\begin{frame}{Open problems in crowdsourcing}
  \begin{itemize}%[<+- | alert@+>]
    \item \textbf{Complexity}~\textcite{suzukiAtelier,KimStoria,yuanAlmost,
                           Nebeling:2016:WCW:2858036.2858169,
                           Hahn:2016:KAB:2858036.2858364}
    \item \textbf{Decomposition}~\textcite{sensitiveTasks,LykourentzouPersonalityMatters,
                              Law:2016:CKC:2858036.2858144,
                              Chang:2016:ACC:2858036.2858411,
                              Newell:2016:OMA:2858036.2858490}
    \item \textbf{Relationships}~\textcite{turkopticon,storiesIraniSilberman,crowdcollab,
                              takingAHITMcInnis}
  \end{itemize}
\end{frame}

\begin{frame}[standout]{whataatatat}
    What is the future of work?

\end{frame}

\begin{frame}{Introduction}
  We hope to provide:
      \begin{itemize}
        \item A useful ontological lens for making sense of crowdsourcing and gig work (which we collectively call ``\textit{on--demand work}'') as a resurgence of \textit{piecework}.
        \item A method for making sense of contemporary phenomena through \textit{historical analysis}.
      \end{itemize}
\end{frame}

\begin{frame}{A case for comparative historical analysis}
Historical analysis is nothing new
    \begin{itemize}
      \item \textcite{Wyche2006,bodker1993historical}
    \end{itemize}
\end{frame}

\begin{frame}{A brief glossary}
    \begin{itemize}
      \item Crowd work: digitally mediated \textbf{information work}
      --- for example, work done on Amazon Mechanical Turk~\cite{crowdworkFuture}
      \item Gig work: digitally mediated --- but often \textbf{physically embodied} --- one--off jobs,
      such as
      \textit{driving},
      \textit{courier services},
      and \textit{administrative support}~\cite{friedman2014workers,Parigi:2016:GE:3026779.3013496}
    \end{itemize}
\end{frame}

\begin{frame}{Complexity}
  What kinds of problems do we mean when we talk about complexity?
  \begin{itemize}
    \item Can crowds improve existing works?~\cite{bernsteinSoylent,Kim:2014:CSI:2556288.2556986}
    \item Can crowds critique designs?~\cite{yuanAlmost}
    \item Can crowds create things from whole cloth?~\cite{KimStoria,Kim2017,Hahn:2016:KAB:2858036.2858364,Lasecki:2014:LSR:2661334.2661352}
  \end{itemize}
\end{frame}

\begin{frame}{What does the crowdsourcing literature say?}
    something pretty insightful I bet!
\end{frame}

\begin{frame}{What does the piecework literature say?}
    something even more insightful, I'm sure!
\end{frame}

\begin{frame}[t]\frametitle{Let's compare this stuff}
\framesubtitle{something else}
  \begin{columns}
  \begin{column}{0.5\textwidth}
  % \section*{Piecework}
     some text here some text here some text here some text here some text here

  \end{column}

  \begin{column}{0.5\textwidth}
  % \section*{CrowdWork}
     some text here some text here some text here some text here some text here

  \end{column}
  \end{columns}
\end{frame}

% \section{Piecework Primer}
% \begin{frame}{Piecework Review
%                                                                                 [\texttt{1 minute}]
% }
% % What is piecework?
% % \begin{figure}

% % \end{figure}
% \end{frame}
